Explaining and exploring the 95% interval metric

### 2020-08-11 analysis/reports/rov_metric.Rmd
manuscript for Morgan

example_fs3 <- readd(fs_s_3_n_34, cache = cache)

example_di3 <- readd(di_fs_s_3_n_34, cache =cache)

@@

>>>>

example_fs3 <- readd(fs_s_4_n_34, cache = cache)

example_di3 <- readd(di_fs_s_4_n_34, cache =cache)

@@

```
```{r fig for manuscript, fig.dim = c(3, 9)}

samples_plots <- list(

  ggplot(example_fs3, aes(rank, abund, group = sim, color = skew)) +
    geom_line(alpha = .25) +
    theme_bw() +
    scale_color_viridis_c(option = "plasma", end = .8) +
    ggtitle(paste0("S = ", (example_fs3$s0), "; N = ", (example_fs3$n0[1])), subtitle = paste0(round(exp(example_fs3$log_nparts[1]), 0), " elements in FS")) +
    theme(legend.position = "top"),

  ggplot(example_fs2, aes(rank, abund, group = sim, color = skew)) +
    geom_line(alpha = .1) +
    theme_bw() +
    scale_color_viridis_c(option = "plasma", end = .8) +
    ggtitle(paste0("S = ", (example_fs2$s0), "; N = ", (example_fs2$n0[1])), subtitle = paste0(round(exp(example_fs2$log_nparts[1]), 0), " elements in FS")) +
    theme(legend.position = "top"),
  ggplot(example_fs, aes(rank, abund, group = sim, color = skew)) +
    geom_line(alpha = .1) +
    theme_bw() +
    scale_color_viridis_c(option = "plasma", end = .8) +
    ggtitle(paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1])), subtitle =  paste0(round(exp(example_fs$log_nparts[1]), 0), " elements in FS")) +
    theme(legend.position = "top")
)

intervals_plots <- list(

  ggplot(example_fs3, aes(skew, ..ndensity..)) +
    geom_density() +
    geom_histogram(bins = 50) +
    theme_bw() +
    geom_vline(xintercept = c(example_fs3$skew_97p5[1], example_fs3$skew_2p5[1]), color = "red") +
    ggtitle(paste0("S = ", (example_fs3$s0), "; N = ", (example_fs3$n0[1])), subtitle =  paste0("Skew 95% ratio: ", round((example_fs3$skew_95_ratio_2t[1]), 2))),

  ggplot(example_fs2, aes(skew, ..ndensity..)) +
    geom_density() +
    geom_histogram(bins = 50) +
    theme_bw() +
    geom_vline(xintercept = c(example_fs2$skew_97p5[1], example_fs2$skew_2p5[1]), color = "red") +
    ggtitle(paste0("S = ", (example_fs2$s0), "; N = ", (example_fs2$n0[1])), subtitle =  paste0("Skew 95% ratio: ", round((example_fs2$skew_95_ratio_2t[1]), 2))),

  ggplot(example_fs, aes(skew, ..ndensity..)) +
    geom_density() +
    geom_histogram(bins = 50) +
    theme_bw() +
    geom_vline(xintercept = c(example_fs$skew_97p5[1], example_fs$skew_2p5[1]), color = "red") +
    ggtitle(paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1])), subtitle =  paste0("Skew 95% ratio: ", round((example_fs$skew_95_ratio_2t[1]), 2)))

)

gridExtra::grid.arrange(grobs = samples_plots, ncol = 1)
gridExtra::grid.arrange(grobs = intervals_plots, ncol = 1)
